---
title: "Create data links and initial QC"
author: "Sam"
date: "11/30/2020"
output:  
  pdf_document: default
  html_document: default
  # word_document: default
  
---

#### Purpose
## this script defines the folders and links the raw data into them and
## also renames them and runs fastqc and multiqc on the raw data
### 
```{r setup, include=FALSE}
knitr::opts_chunk$set(engine.opts = list(bash = "-l"), include = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(ezknitr)
# Set data/output directories
data_dir <- "./data_links/"
output_dir <- "./r_output/"
figure_dir <- "./r_output/figures"
reports_dir <- "./r_output/reports"
rds_obj_dir <- "./r_output/intermediate_files"

#you will need some of these system packages installed locally
# rename 
# fastqc
# multiqc

```

```{r}
getwd()

```
#### 1. Make some directories
### - create directories
```{bash, engine.opts = "-l"}
if [ ! -d ./data_links ]; then
    echo "directory missing, creating it";
    mkdir ./data_links
  else
    echo "data_links directory exists"
fi

if ! test -d ./r_output ; then
    echo "directory missing, creating it";
    mkdir ./r_output
  else
    echo "r_ouput directory exists"
fi
```

#### 2. Make soft links to data (you will need to update file path)
### - create raw data links (you will need to update file path)
```{bash}
if  [[ ! $(ls -L ./data_links/*fq.gz) ]]; then
    echo "links missing, creating them"
    
    find  ~/Desktop/data/Gen_core_UM_noDemux_2017/elk_microB_time_series_raw/ -iname "*.fq*" -printf "%P\n " | xargs  -I % -n1 ln -s  ~/Desktop/data/Gen_core_UM_noDemux_2017/elk_microB_time_series_raw/% ~/Desktop/projects/time_series/data_links/%

    echo "files exists"
fi
```

run fastqc and multiQC.. check directory
```{bash}
if [ ! -d ./data_links/fastqc_reports ]; then
    echo "directory missing, creating it...";
    mkdir ./data_links/fastqc_reports
  else
    echo "fastqc directory exists.";
fi
```

```{r}
Sys.setenv("DISPLAY"=":50")
```

run fastqc or multiQC
```{bash}
if  [[ ! $(ls ./data_links/fastqc_reports/*fastqc.html) ]]; then
    echo "fastqc output missing, running fastqc...";
  find ./data_links/ -name "*fq.gz" | xargs -n 1 fastqc -t 25 -o ./data_links/fastqc_reports/
  else
    echo "fastqc output exists. Checking for multiQC...";
fi
```

run multiQC
```{bash}
if   [ ! -d ./r_output/reports/multiqc_data ]; then
    echo "multiqc output missing, running multiqc...";
    mkdir ./r_output/reports/
  else
    echo "multiqc output exists.";
fi
```

```{bash, engine.opts = "-l"}
 multiqc ./data_links/fastqc_reports/. -o ./r_output/reports
```
# done
